A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2019-02-14 reviewer_response.tex

Associate Editor

Fluid Phase Equlibria
\vspace{0.3cm}

Dear Prof. Jeffrey Potoff:

\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}.
We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text.
The most substantial revision took place in section 5.3, for which we carried out additional simulations.
In addition, we have included the full names of the ionic liquids in the abstract. To facilitate your evaluation, we have crossed out all removed text and incorporated new content in color blue.

### 2019-02-19 ionic_liquids.tex
Changes in the review: pressure calculation

\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\modulolinenumbers[5]
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{natbib}
\usepackage[version=4]{mhchem}
\usepackage{adjustbox}   
\usepackage[position=top,captionskip=0pt]{subfig}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.eps,.png}

@@

\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}

@@

\begin{abstract}
In this paper, we calculate solvation free energies of several compounds in ionic liquids.
These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required in the design of environmentally sustainable processes.
It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
Recently, the propensity of the ionic liquid 1-ethyl-3-methylimidazolium tetracyanoborate (\ce{[emim][B(CN)_4]}) for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and 1-ethyl-3-methylimidazolium bis (trifluoromethylsulfonyl) imide (\ce{[emim][Tf_2N]}) are carried out both at infinite dilution and at high concentrations.
A systematic study is performed by comparing several force fields and assessing the efficacy of simplifications in the simulations by using rigid-body dynamics and pairwise electrostatics.
Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
\end{abstract}

@@

Recently, Carvalho \textit{et al}. \cite{Carvalho_2016} called into question the potentiality of ILs for \ce{CO_2} capture.
They warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposedly high absorption capability of certain ILs.
Although most thermodynamic models are formulated in terms of molar fractions, a key factor that dictates the efficiency of absorption process  is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
By expressing the solubility values in terms of molality and performing an exhaustive comparison among various ILs, Carvalho \textit{et al}. \cite{Carvalho_2016} show that most systems which promote physical absorption of \ce{CO_2} exhibit solubilities which are similar, or even lower, than that observed for heavy alkanes such as eicosane.
This is true for the popular ILs \ce{[bmim][Tf_2N]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][Tf_2N]} and \ce{[hmim][pFAP]}.
The only exception they found was the family of ILs containing the anion \ce{[B(CN)_4]^-} (tetracyanoborate).

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
In this context, molecular simulation provides us with a powerful tool for studying solvation processes.
To the best of our knowledge, only one study in the literature reports computation of solvation free energy for \ce{CO_2} in \ce{[emim][B(CN)_4]} by molecular simulation \cite{Liu_2014_1}.
Nonetheless, the computed value is overestimated, as observed by deriving a Henry's law constant and comparing it to available experimental data.
Such scarcity motivated us to carry out the present investigation, in which we have evaluated different force fields for \ce{[emim][B(CN)_4]} proposed in the literature.
As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][Tf_2N]}, both at infinite dilution and at high concentrations.
The simulations confirmed what is observed in experiments.
For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given mass of solvent.
In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
The solutes we considered were hexane, benzene, cyclohexane, ethanol, and water.

@@

Two additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems investigated) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

The equilibrium pressure will be the intersection point between the function $\Delta G_{\text{solv}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, and $\Delta G_{\text{sim}} (p)$, as obtained in simulations. Note that besides  $\Delta G_{\text{sim}}$, we are taking into account variations of $c_s$ with pressure. These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states. This implies a significant reduction in computational cost. In particular, we use the Multistate Bennett Acceptance Ratio (MBAR) estimator \cite{Shirts_2008}, which has been successfully used for the purpose of reweighing ~\cite{Aimoli2014, Nichele2018, Schieber2018}.

@@

In the case of ionic liquid \ce{[emim][Tf_2N]}, we use the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][Tf_2N]} at several temperatures.

@@

In the case of $\Delta G_\text{vdW}$, the Expanded Ensemble method \cite{Lyubartsev_1992} is applied for sampling the whole $\lambda_\text{vdW}$ set in a single simulation.
An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{vdW}$.
In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, p, T, and $\lambda_\text{vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{vdW}$.
The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
In addition, a set of biasing weights is included in the MC acceptance criterion, thus making it possible to enhance the sampling procedure by iteratively tuning these weights until all $\lambda_\text{vdW}$ states are visited with equal frequency \cite{Lyubartsev_1992}.
Given that sample decorrelation is improved by having short MD runs between MC transitions \cite{Chodera_2011_2}, we used only 5 steps in each run.
In the iteration process for tuning the biasing weights, the simulation times for the preliminary and the final expanded ensemble rounds are 10 and 40 ns, respectively.
In this way, 3 iterations were sufficient in all cases for attaining, in the final round, an acceptable uncertainty in $\Delta G_\text{sim}$ estimated via MBAR \cite{Shirts_2008, Klimovich_2015}. Considering also the MD runs at each $\lambda_{\text{Coul}}$, the simulation time was 110 ns for each system.

@@

In this section, we analyze the possibility of introducing simplifications in the molecular modeling and simulation of ionic liquids without substantially affecting the resulting thermodynamics properties.
For this, we compare results obtained with a \textit{standard} methodology to those obtained with a \textit{simplified} one.
The standard setup comprises simulating ions with moving bonds, angles, and dihedrals and using the Particle-Particle/Particle-Mesh (PPPM) Ewald method \cite{Hockney_1988} for calculating the Coulomb interactions.
In this case, a real-space cutoff of $12~\text{\AA}$ and a tolerance of $10^{-4}$ are used in LAMMPS for automatic determination of PPPM parameters such as damping factor and FFT grid spacing.
In the simplified setup, the ions are modeled as rigid bodies and the DSF method \cite{Fennell2006} with $r_c = 12 ~\text{\AA}$ and $\alpha = 0.2 ~\text{\AA}^{-1}$) is used as and alternative to the PPPM scheme.
For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[Tf_2N]^-}, whose flexibility could lead to significant conformational changes.
On the other hand, small and highly symmetric anions such as \ce{PF_6} and \ce{BF_4} are already usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.

As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[Tf_2N]^-}.
Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{atoms_id.pdf}
\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[Tf_2N]^-}).}
\label{fig:atoms_id}
\end{figure}

@@

A study of conformations was also carried out for \ce{[emim][Tf_2N]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][Tf_2N]}.
This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
With regard to the anion \ce{[Tf_2N]^-}, Deetlefs \textit{et al}. \cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[Tf_2N]^-} is mostly found in its \textit{trans} conformation.
In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[Tf_2N]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
This CDF also makes clear that \ce{[Tf_2N]^-} exhibits a considerable degree of flexibility.
Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Ludwig_anion}
\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.}
\label{fig:die_ntf2}
\end{figure}

\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
\label{sec:henry_results}

In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}. These should be compared to the experimental data reported by Mahurin \textit{et al}. \cite{Mahurin_2010} ($K_s = 3.941 \pm 0.003 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}. \cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
Uncertainties in $K_s$ were calculated using a standard error propagation formula, given by
\begin{equation}
\delta K_s = \beta K_s \sqrt{\left[ \delta^2 (\Delta G_{\text{vdW}}) + \delta^2(\Delta G_{\text{Coul}}) \right]},
\end{equation}
with uncertainties in free energy calculate using MBAR \cite{Shirts_2008}.

>>>>

%\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\modulolinenumbers[5]
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{natbib}
\usepackage[version=4]{mhchem}
\usepackage{adjustbox}   
\usepackage[position=top,captionskip=0pt]{subfig}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.eps,.png}

@@

\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}

@@

\begin{abstract}
In this paper, we calculate solvation free energies of several compounds in ionic liquids.
These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required in the design of environmentally sustainable processes.
It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
Recently, the propensity of the ionic liquid 1-ethyl-3-methylimidazolium tetracyanoborate (\ce{[emim][B(CN)_4]}) for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and 1-ethyl-3-methylimidazolium bis (trifluoromethylsulfonyl) imide (\ce{[emim][NTf_2]}) are carried out both at infinite dilution and at high concentrations.
A systematic study is performed by comparing several force fields and assessing the efficacy of simplifications in the simulations by using rigid-body dynamics and pairwise electrostatics.
Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
\end{abstract}

@@

Recently, Carvalho \textit{et al}. \cite{Carvalho_2016} called into question the potentiality of ILs for \ce{CO_2} capture.
They warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposedly high absorption capability of certain ILs.
Although most thermodynamic models are formulated in terms of molar fractions, a key factor that dictates the efficiency of absorption process  is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
By expressing the solubility values in terms of molality and performing an exhaustive comparison among various ILs, Carvalho \textit{et al}. \cite{Carvalho_2016} show that most systems which promote physical absorption of \ce{CO_2} exhibit solubilities which are similar, or even lower, than that observed for heavy alkanes such as eicosane.
This is true for the popular ILs \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}.
The only exception they found was the family of ILs containing the anion \ce{[B(CN)_4]^-} (tetracyanoborate).

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
In this context, molecular simulation provides us with a powerful tool for studying solvation processes.
To the best of our knowledge, only one study in the literature reports computation of solvation free energy for \ce{CO_2} in \ce{[emim][B(CN)_4]} by molecular simulation \cite{Liu_2014_1}.
Nonetheless, the computed value is overestimated, as observed by deriving a Henry's law constant and comparing it to available experimental data.
Such scarcity motivated us to carry out the present investigation, in which we have evaluated different force fields for \ce{[emim][B(CN)_4]} proposed in the literature.
As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
The simulations confirmed what is observed in experiments.
For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given mass of solvent.
In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
The solutes we considered were hexane, benzene, cyclohexane, ethanol, and water.

@@

Two additional assumptions are made here. First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems we investigate here) or can be approximated by an ideal solution. Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase. In this case, Eq.~\eqref{eq:fgas_d} becomes
\begin{equation}
\label{eq:equilibrium pressure}
y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
\end{equation}
where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.

To determine the equilibrium condition, it is necessary to know how $\Delta G_{\text{sim}}$ and $c_s$ vary with pressure, so that Eqs.~\eqref{eq:free_solv} and \eqref{eq:equilibrium pressure} can be solved together.
Fortunately, the Multistate Bennett Acceptance Ratio (MBAR) method \cite{Shirts_2008} allows us to combine simulation samples obtained at discrete thermodynamic states and compute interpolated expectation values along a continuous range of unsampled states.
This technique, known as reweighting \cite{McDonald1967,McDonald1969}, has been successfully employed in previous work \cite{Aimoli2014, Nichele2018, Schieber2018}, where one can find more details about the calculation procedure.
Here, we carry out solvation simulations at a few pressures in the vicinity of the experimental value and employ MBAR to determine both functions $\Delta G_{\text{sim}}(p)$ and $c_s(p)$.

@@

In the case of ionic liquid \ce{[emim][NTf_2]}, we use the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][NTf_2]} at several temperatures.

@@

In the case of $\Delta G_\text{vdW}$, the Expanded Ensemble method \cite{Lyubartsev_1992} is applied for sampling the whole $\lambda_\text{vdW}$ set in a single simulation.
An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{vdW}$.
In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, p, T, and $\lambda_\text{vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{vdW}$.
The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
In addition, a set of biasing weights is included in the MC acceptance criterion, thus making it possible to enhance the sampling procedure by iteratively tuning these weights until all $\lambda_\text{vdW}$ states are visited with equal frequency \cite{Lyubartsev_1992}.
Given that sample decorrelation is improved by having short MD runs between MC transitions \cite{Chodera_2011_2}, we used only 5 steps in each run.
In the iteration process for tuning the biasing weights, the simulation times for the preliminary and the final expanded ensemble rounds are 10 and 40 ns, respectively.
In this way, 3 iterations were sufficient in all cases for attaining, in the final round, an acceptable uncertainty in $\Delta G_\text{sim}$ estimated via MBAR \cite{Shirts_2008, Klimovich_2015}. Considering also the MD runs at each $\lambda_{\text{Coul}}$, the simulation time was $110~\mathrm{ns}$ for each system.

@@

In this section, we analyze the possibility of introducing simplifications in the molecular modeling and simulation of ionic liquids without substantially affecting the resulting thermodynamics properties.
For this, we compare results obtained with a \textit{standard} methodology to those obtained with a \textit{simplified} one.
The standard setup comprises simulating ions with moving bonds, angles, and dihedrals and using the Particle-Particle/Particle-Mesh (PPPM) Ewald method \cite{Hockney_1988} for calculating the Coulomb interactions.
In this case, a real-space cutoff of $12~\text{\AA}$ and a tolerance of $10^{-4}$ are used in LAMMPS for automatic determination of PPPM parameters such as damping factor and FFT grid spacing.
In the simplified setup, the ions are modeled as rigid bodies and the DSF method \cite{Fennell2006} with $r_c = 12 ~\text{\AA}$ and $\alpha = 0.2 ~\text{\AA}^{-1}$) is used as and alternative to the PPPM scheme.
For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[NTf_2]^-}, whose flexibility could lead to significant conformational changes.
On the other hand, small and highly symmetric anions such as \ce{PF_6} and \ce{BF_4} are already usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.

As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{atoms_id.pdf}
\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
\label{fig:atoms_id}
\end{figure}

@@

A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][NTf_2]}.
This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
With regard to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}. \cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly found in its \textit{trans} conformation.
In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[NTf_2]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
This CDF also makes clear that \ce{[NTf_2]^-} exhibits a considerable degree of flexibility.
Due to this observed behaviors of both ions, all simulations of \ce{[emim][NTf_2]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Ludwig_anion}
\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.}
\label{fig:die_ntf2}
\end{figure}

\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
\label{sec:henry_results}

In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}. These should be compared to the experimental data reported by Mahurin \textit{et al}. \cite{Mahurin_2010} ($K_s = 3.941 \pm 0.003 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}. \cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][NTf_2]}).
Uncertainties in $K_s$ were calculated using a standard error propagation formula, given by
\begin{equation}
\delta K_s = \beta K_s \sqrt{\left[ \delta^2 (\Delta G_{\text{vdW}}) + \delta^2(\Delta G_{\text{Coul}}) \right]},
\end{equation}
with the uncertainties in free energies calculated by MBAR \cite{Shirts_2008}.

\begin{table*}
	\centering
	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$. The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][NTf_2]} are, respectively, $3.941 \pm 0.003 ~\mathrm{MPa}$ \cite{Mahurin_2010} and $3.95 \pm 0.01 ~\mathrm{MPa}$ \cite{Finotello_2008}.}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{ccccccc}  
			\hline\hline
			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (MPa)  & (\%) \\
			\hline
%			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}: $K_{s}^{\text{exp}} = 38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010}} \\
			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}} \\
			Koller \textit{et al}. \cite{Koller_2012} & $4.5925$ & $0.45 \pm 0.01$ & $-1.06 \pm 0.02$ & $-0.61 \pm 0.02$ & $ 4.1 \pm 0.1$ & $2.8$ \\
			Batista \textit{et al}. \cite{Batista_2015} & $4.3700$ & $0.378 \pm 0.008$ & $-1.24 \pm 0.01$  & $-0.86 \pm 0.01$ & $2.52 \pm 0.05$ & $38.9$ \\
			Liu \textit{et al}. \cite{Liu_2014} & $4.3815$ & $0.226 \pm 0.009$ & $-1.11 \pm 0.01$ & $-0.88 \pm 0.01$ & $2.46 \pm 0.05$ & $37.6$  \\
			Weber and Kirchner \cite{Weber_2016} & $4.5221$ & $0.478 \pm 0.009$ & $-1.23 \pm 0.02$ & $-0.75 \pm 0.02$ & $3.1 \pm 0.1$ & $20.3$  \\
			\hline
%			\multicolumn{7}{c}{\ce{[emim][NTf_2]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
			\multicolumn{7}{c}{\ce{[emim][NTf_2]}} \\
			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $3.99\pm 0.05$  & $0.97$  \\
			\hline\hline
			\label{table:henry} 
		\end{tabular}
	\end{adjustbox}
\end{table*}

Is it worth remarking that the result of $\Delta G_\text{sim}$ obtained with the model of Liu \textit{et al}. \cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{vdW}$ and $\lambda_\text{Coul}$.
Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][NTf_2]} is very close to the one obtained by Kerl \textit{et al}. \cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no reported uncertainty) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
%These consistencies have served for validating the methodological approaches of this work.
